\textbf{Preprinting Microbiology}

### 2017-03-14 submission/Schloss_PrePrints_mBio_2017.tex
Render prior to submission

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Preprinting Microbiology},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

@@

\textbf{Number of words:} \textasciitilde4500 plus references, figures, and abstract

@@

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
comments on earlier versions of this manuscript and to the numerous
individuals who provided feedback on the preprint version of the
manuscript. This work was supported in part by funding from the National
Institutes of Health (P30DK034933). I appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The workflow utilized
commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
Within R I utilized the cowplot (v.0.6.3), dplyr (v.0.5.0), ggplot2
(v.2.2.0.9000), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
rjson (v.0.2.15), rvest (v.0.3.2.9000), sportcolors (v.0.0.1), and tidyr
(v.0.6.0) packages. A reproducible version of this manuscript and
analysis is available at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.

@@

\includegraphics[width=3.5in]{../figures/figure1.png}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\hypertarget{ref-Vale2015}{}
1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
biology. Proceedings of the National Academy of Sciences
\textbf{112}:13439--13446.
doi:\href{https://doi.org/10.1073/pnas.1511912112}{10.1073/pnas.1511912112}.

\hypertarget{ref-DesjardinsProulx2013}{}
2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
\textbf{Ram K}, \textbf{Poisot T}, \textbf{Gravel D}. 2013. The case for
open preprints in biology. PLoS Biology \textbf{11}:e1001563.
doi:\href{https://doi.org/10.1371/journal.pbio.1001563}{10.1371/journal.pbio.1001563}.

\hypertarget{ref-Berg2016}{}
3. \textbf{Berg JM}, \textbf{Bhalla N}, \textbf{Bourne PE},
\textbf{Chalfie M}, \textbf{Drubin DG}, \textbf{Fraser JS},
\textbf{Greider CW}, \textbf{Hendricks M}, \textbf{Jones C},
\textbf{Kiley R}, \textbf{King S}, \textbf{Kirschner MW},
\textbf{Krumholz HM}, \textbf{Lehmann R}, \textbf{Leptin M},
\textbf{Pulverer B}, \textbf{Rosenzweig B}, \textbf{Spiro JE},
\textbf{Stebbins M}, \textbf{Strasser C}, \textbf{Swaminathan S},
\textbf{Turner P}, \textbf{Vale RD}, \textbf{VijayRaghavan K},
\textbf{Wolberger C}. 2016. Preprints for the life sciences. Science
\textbf{352}:899--901.
doi:\href{https://doi.org/10.1126/science.aaf9133}{10.1126/science.aaf9133}.

\hypertarget{ref-Bhalla2016}{}
4. \textbf{Bhalla N}. 2016. Has the time come for preprints in biology?
Molecular Biology of the Cell \textbf{27}:1185--1187.
doi:\href{https://doi.org/10.1091/mbc.e16-02-0123}{10.1091/mbc.e16-02-0123}.

\hypertarget{ref-Nature1966}{}
5. 1966. Preprints galore. Nature \textbf{211}:897--898.
doi:\href{https://doi.org/10.1038/211897a0}{10.1038/211897a0}.

\hypertarget{ref-Ginsparg2011}{}
6. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
doi:\href{https://doi.org/10.1038/476145a}{10.1038/476145a}.

\hypertarget{ref-Shuai2012}{}
7. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
scientific community reacts to newly submitted preprints: Article
downloads, twitter mentions, and citations. PLoS ONE \textbf{7}:e47523.
doi:\href{https://doi.org/10.1371/journal.pone.0047523}{10.1371/journal.pone.0047523}.

\hypertarget{ref-Callaway2013}{}
8. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
bring preprints to life. Nature Medicine \textbf{19}:512--512.
doi:\href{https://doi.org/10.1038/nm0513-512}{10.1038/nm0513-512}.

\hypertarget{ref-Angell1991}{}
9. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
revisited. New England Journal of Medicine \textbf{325}:1371--1373.
doi:\href{https://doi.org/10.1056/nejm199111073251910}{10.1056/nejm199111073251910}.

\hypertarget{ref-ICMJE}{}
10. Recommendations for the conduct, reporting, editing, and publication
of scholarly work in medical journals.
\url{http://www.icmje.org/news-and-editorials/icmje-recommendations_annotated_dec16.pdf}.

\hypertarget{ref-PreprintPolicy}{}
11. List of academic journals by preprint policy.
\url{https://en.wikipedia.org/wiki/List_of_academic_journals_by_preprint_policy}.

\hypertarget{ref-Sherpa}{}
12. Publisher copyright policies \& self-archiving.
\url{http://www.sherpa.ac.uk/romeo/index.php}.

\hypertarget{ref-Drubin2016}{}
13. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
articles and why MBoC quickly embraced preprints. Molecular Biology of
the Cell \textbf{27}:3181--3182.
doi:\href{https://doi.org/10.1091/mbc.e16-09-0651}{10.1091/mbc.e16-09-0651}.

\hypertarget{ref-Spier2002}{}
14. \textbf{Spier R}. 2002. The history of the peer-review process.
Trends in Biotechnology \textbf{20}:357--358.
doi:\href{https://doi.org/10.1016/s0167-7799(02)01985-6}{10.1016/s0167-7799(02)01985-6}.

\hypertarget{ref-Burnham1990}{}
15. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
JAMA: The Journal of the American Medical Association \textbf{263}:1323.
doi:\href{https://doi.org/10.1001/jama.1990.03440100023003}{10.1001/jama.1990.03440100023003}.

\hypertarget{ref-Pulverer2016}{}
16. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
\textbf{35}:2617--2619.
doi:\href{https://doi.org/10.15252/embj.201670030}{10.15252/embj.201670030}.

\hypertarget{ref-Loew2016}{}
17. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
\textbf{111}:E01--E02.
doi:\href{https://doi.org/10.1016/j.bpj.2016.06.035}{10.1016/j.bpj.2016.06.035}.

\hypertarget{ref-Vale2016}{}
18. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
the life sciences. eLife \textbf{5}.
doi:\href{https://doi.org/10.7554/elife.16931}{10.7554/elife.16931}.

\hypertarget{ref-Dolgin2016}{}
19. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
Nature.
doi:\href{https://doi.org/10.1038/nature.2016.21074}{10.1038/nature.2016.21074}.

\hypertarget{ref-SinghChawla2017}{}
20. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
Nature.
doi:\href{https://doi.org/10.1038/nature.2017.21333}{10.1038/nature.2017.21333}.

\hypertarget{ref-Black2017}{}
21. \textbf{Black A}, \textbf{Potter B}, \textbf{Dudas G},
\textbf{Feldstein L}, \textbf{Grubaugh ND}, \textbf{Andersen KG},
\textbf{Ellis BR}, \textbf{Ellis EM}, \textbf{Bedford T}. 2017. Genetic
characterization of the zika virus epidemic in the us virgin islands.
bioRxiv 113100.

\hypertarget{ref-Afshinnekoo2015a}{}
22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Geospatial resolution of human
and bacterial diversity with city-scale metagenomics. Cell Systems
\textbf{1}:72--87.
doi:\href{https://doi.org/10.1016/j.cels.2015.01.001}{10.1016/j.cels.2015.01.001}.

\hypertarget{ref-Petit2015}{}
23. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
\textbf{Read TD}. 2015. Searching for anthrax in the New York City
subway metagenome.
doi:\href{https://doi.org/10.5281/zenodo.17158}{10.5281/zenodo.17158}.

\hypertarget{ref-Ackelsberg2015}{}
24. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
\textbf{Petersen J}, \textbf{Mead P}, \textbf{Schriefer M},
\textbf{Kingry L}, \textbf{Hoffmaster A}, \textbf{Gee JE}. 2015. Lack of
evidence for plague or anthrax on the new york city subway. Cell Systems
\textbf{1}:4--5.
doi:\href{https://doi.org/10.1016/j.cels.2015.07.008}{10.1016/j.cels.2015.07.008}.

\hypertarget{ref-Afshinnekoo2015b}{}
25. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Modern methods for delineating
metagenomic complexity. Cell Systems \textbf{1}:6--7.
doi:\href{https://doi.org/10.1016/j.cels.2015.07.007}{10.1016/j.cels.2015.07.007}.

\hypertarget{ref-Boothby2015}{}
26. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
\textbf{Wang JR}, \textbf{Patanella KA}, \textbf{Nishimura EO},
\textbf{Tintori SC}, \textbf{Li Q}, \textbf{Jones CD}, \textbf{Yandell
M}, \textbf{Messina DN}, \textbf{Glasscock J}, \textbf{Goldstein B}.
2015. Evidence for extensive horizontal gene transfer from the draft
genome of a tardigrade. Proceedings of the National Academy of Sciences
\textbf{112}:15976--15981.
doi:\href{https://doi.org/10.1073/pnas.1510461112}{10.1073/pnas.1510461112}.

\hypertarget{ref-Koutsovoulos2016a}{}
27. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
\textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
H}, \textbf{Thomas F}, \textbf{Aboobaker A}, \textbf{Blaxter M}. 2016.
No evidence for extensive horizontal gene transfer in the genome of the
tardigrade hypsibius dujardini. bioRxiv 033464.
doi:\href{https://doi.org/10.1101/033464}{10.1101/033464}.

\hypertarget{ref-Boothby2016}{}
28. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
al. and arakawa: Identifying foreign genes in independentHypsibius
dujardinigenome assemblies. Proceedings of the National Academy of
Sciences \textbf{113}:E3058--E3061.
doi:\href{https://doi.org/10.1073/pnas.1601149113}{10.1073/pnas.1601149113}.

\hypertarget{ref-Koutsovoulos2016b}{}
29. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
\textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
H}, \textbf{Thomas F}, \textbf{Aboobaker AA}, \textbf{Blaxter M}. 2016.
No evidence for extensive horizontal gene transfer in the genome of the
tardigradeHypsibius dujardini. Proceedings of the National Academy of
Sciences \textbf{113}:5053--5058.
doi:\href{https://doi.org/10.1073/pnas.1600338113}{10.1073/pnas.1600338113}.

\hypertarget{ref-Bemm2016}{}
30. \textbf{Bemm F}, \textbf{Weiß CL}, \textbf{Schultz J},
\textbf{Förster F}. 2016. Genome of a tardigrade: Horizontal gene
transfer or bacterial contamination? Proceedings of the National Academy
of Sciences \textbf{113}:E3054--E3056.
doi:\href{https://doi.org/10.1073/pnas.1525116113}{10.1073/pnas.1525116113}.

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Preprinting Microbiology},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\textbf{Number of words:} \textasciitilde5400 plus references, figures, and abstract

@@

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful
comments on earlier versions of this manuscript and to the numerous
individuals who provided feedback on the preprint version of the
manuscript. This work was supported in part by funding from the National
Institutes of Health (P30DK034933). I appreciate the support of
Altmetric, Inc and Thompson Reuters who provided advanced programming
interface (API) access to their databases. The workflow utilized
commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.3.3.2).
Within R I utilized the cowplot (v.0.6.9990), dplyr (v.0.5.0), ggplot2
(v.2.1.0.9001), httr (v.1.2.1), RCurl (v.1.95-4.8), rentrez (v.1.0.4),
rjson (v.0.2.15), rvest (v.0.3.2), sportcolors (v.0.0.1), and tidyr
(v.0.6.0) packages. A reproducible version of this manuscript and
analysis is available at
\url{http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017}.

@@

@@

\hyperdef{}{references}{\label{references}}
\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

\hyperdef{}{ref-Vale2015}{\label{ref-Vale2015}}
1. \textbf{Vale RD}. 2015. Accelerating scientific publication in
biology. Proceedings of the National Academy of Sciences
\textbf{112}:13439--13446.
doi:\url{http://doi.org/10.1073/pnas.1511912112}.

\hyperdef{}{ref-DesjardinsProulx2013}{\label{ref-DesjardinsProulx2013}}
2. \textbf{Desjardins-Proulx P}, \textbf{White EP}, \textbf{Adamson JJ},
\textbf{Ram K}, \textbf{Poisot T}, \textbf{Gravel D}. 2013. The case for
open preprints in biology. PLoS Biology \textbf{11}:e1001563.
doi:\url{http://doi.org/10.1371/journal.pbio.1001563}.

\hyperdef{}{ref-Berg2016}{\label{ref-Berg2016}}
3. \textbf{Berg JM}, \textbf{Bhalla N}, \textbf{Bourne PE},
\textbf{Chalfie M}, \textbf{Drubin DG}, \textbf{Fraser JS},
\textbf{Greider CW}, \textbf{Hendricks M}, \textbf{Jones C},
\textbf{Kiley R}, \textbf{King S}, \textbf{Kirschner MW},
\textbf{Krumholz HM}, \textbf{Lehmann R}, \textbf{Leptin M},
\textbf{Pulverer B}, \textbf{Rosenzweig B}, \textbf{Spiro JE},
\textbf{Stebbins M}, \textbf{Strasser C}, \textbf{Swaminathan S},
\textbf{Turner P}, \textbf{Vale RD}, \textbf{VijayRaghavan K},
\textbf{Wolberger C}. 2016. Preprints for the life sciences. Science
\textbf{352}:899--901. doi:\url{http://doi.org/10.1126/science.aaf9133}.

\hyperdef{}{ref-Bhalla2016}{\label{ref-Bhalla2016}}
4. \textbf{Bhalla N}. 2016. Has the time come for preprints in biology?
Molecular Biology of the Cell \textbf{27}:1185--1187.
doi:\url{http://doi.org/10.1091/mbc.e16-02-0123}.

\hyperdef{}{ref-Nature1966}{\label{ref-Nature1966}}
5. 1966. Preprints galore. Nature \textbf{211}:897--898.
doi:\url{http://doi.org/10.1038/211897a0}.

\hyperdef{}{ref-Ginsparg2011}{\label{ref-Ginsparg2011}}
6. \textbf{Ginsparg P}. 2011. ArXiv at 20. Nature \textbf{476}:145--147.
doi:\url{http://doi.org/10.1038/476145a}.

\hyperdef{}{ref-Shuai2012}{\label{ref-Shuai2012}}
7. \textbf{Shuai X}, \textbf{Pepe A}, \textbf{Bollen J}. 2012. How the
scientific community reacts to newly submitted preprints: Article
downloads, twitter mentions, and citations. PLoS ONE \textbf{7}:e47523.
doi:\url{http://doi.org/10.1371/journal.pone.0047523}.

\hyperdef{}{ref-Callaway2013}{\label{ref-Callaway2013}}
8. \textbf{Callaway E}. 2013. Biomedical journal and publisher hope to
bring preprints to life. Nature Medicine \textbf{19}:512--512.
doi:\url{http://doi.org/10.1038/nm0513-512}.

\hyperdef{}{ref-Angell1991}{\label{ref-Angell1991}}
9. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
revisited. New England Journal of Medicine \textbf{325}:1371--1373.
doi:\url{http://doi.org/10.1056/nejm199111073251910}.

\hyperdef{}{ref-ICMJE}{\label{ref-ICMJE}}
10. Recommendations for the conduct, reporting, editing, and publication
of scholarly work in medical journals.
\url{http://www.icmje.org/news-and-editorials/icmje-recommendations_annotated_dec16.pdf}.

\hyperdef{}{ref-PreprintPolicy}{\label{ref-PreprintPolicy}}
11. List of academic journals by preprint policy.
\url{https://en.wikipedia.org/wiki/List_of_academic_journals_by_preprint_policy}.

\hyperdef{}{ref-Sherpa}{\label{ref-Sherpa}}
12. Publisher copyright policies \& self-archiving.
\url{http://www.sherpa.ac.uk/romeo/index.php}.

\hyperdef{}{ref-Drubin2016}{\label{ref-Drubin2016}}
13. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
articles and why MBoC quickly embraced preprints. Molecular Biology of
the Cell \textbf{27}:3181--3182.
doi:\url{http://doi.org/10.1091/mbc.e16-09-0651}.

\hyperdef{}{ref-Spier2002}{\label{ref-Spier2002}}
14. \textbf{Spier R}. 2002. The history of the peer-review process.
Trends in Biotechnology \textbf{20}:357--358.
doi:\url{http://doi.org/10.1016/s0167-7799(02)01985-6}.

\hyperdef{}{ref-Burnham1990}{\label{ref-Burnham1990}}
15. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
JAMA: The Journal of the American Medical Association \textbf{263}:1323.
doi:\url{http://doi.org/10.1001/jama.1990.03440100023003}.

\hyperdef{}{ref-Pulverer2016}{\label{ref-Pulverer2016}}
16. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
\textbf{35}:2617--2619.
doi:\url{http://doi.org/10.15252/embj.201670030}.

\hyperdef{}{ref-Loew2016}{\label{ref-Loew2016}}
17. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
\textbf{111}:E01--E02.
doi:\url{http://doi.org/10.1016/j.bpj.2016.06.035}.

\hyperdef{}{ref-Vale2016}{\label{ref-Vale2016}}
18. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
the life sciences. eLife \textbf{5}.
doi:\url{http://doi.org/10.7554/elife.16931}.

\hyperdef{}{ref-Dolgin2016}{\label{ref-Dolgin2016}}
19. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
Nature. doi:\url{http://doi.org/10.1038/nature.2016.21074}.

\hyperdef{}{ref-SinghChawla2017}{\label{ref-SinghChawla2017}}
20. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
Nature. doi:\url{http://doi.org/10.1038/nature.2017.21333}.

\hyperdef{}{ref-Black2017}{\label{ref-Black2017}}
21. \textbf{Black A}, \textbf{Potter B}, \textbf{Dudas G},
\textbf{Feldstein L}, \textbf{Grubaugh ND}, \textbf{Andersen KG},
\textbf{Ellis BR}, \textbf{Ellis EM}, \textbf{Bedford T}. 2017. Genetic
characterization of the zika virus epidemic in the uS virgin islands.
bioRxiv 113100.

\hyperdef{}{ref-Afshinnekoo2015a}{\label{ref-Afshinnekoo2015a}}
22. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Geospatial resolution of human
and bacterial diversity with city-scale metagenomics. Cell Systems
\textbf{1}:72--87. doi:\url{http://doi.org/10.1016/j.cels.2015.01.001}.

\hyperdef{}{ref-Petit2015}{\label{ref-Petit2015}}
23. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
\textbf{Read TD}. 2015. Searching for anthrax in the New York City
subway metagenome. doi:\url{http://doi.org/10.5281/zenodo.17158}.

\hyperdef{}{ref-Ackelsberg2015}{\label{ref-Ackelsberg2015}}
24. \textbf{Ackelsberg J}, \textbf{Rakeman J}, \textbf{Hughes S},
\textbf{Petersen J}, \textbf{Mead P}, \textbf{Schriefer M},
\textbf{Kingry L}, \textbf{Hoffmaster A}, \textbf{Gee JE}. 2015. Lack of
evidence for plague or anthrax on the new york city subway. Cell Systems
\textbf{1}:4--5. doi:\url{http://doi.org/10.1016/j.cels.2015.07.008}.

\hyperdef{}{ref-Afshinnekoo2015b}{\label{ref-Afshinnekoo2015b}}
25. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Modern methods for delineating
metagenomic complexity. Cell Systems \textbf{1}:6--7.
doi:\url{http://doi.org/10.1016/j.cels.2015.07.007}.

\hyperdef{}{ref-Boothby2015}{\label{ref-Boothby2015}}
26. \textbf{Boothby TC}, \textbf{Tenlen JR}, \textbf{Smith FW},
\textbf{Wang JR}, \textbf{Patanella KA}, \textbf{Nishimura EO},
\textbf{Tintori SC}, \textbf{Li Q}, \textbf{Jones CD}, \textbf{Yandell
M}, \textbf{Messina DN}, \textbf{Glasscock J}, \textbf{Goldstein B}.
2015. Evidence for extensive horizontal gene transfer from the draft
genome of a tardigrade. Proceedings of the National Academy of Sciences
\textbf{112}:15976--15981.
doi:\url{http://doi.org/10.1073/pnas.1510461112}.

\hyperdef{}{ref-Koutsovoulos2016a}{\label{ref-Koutsovoulos2016a}}
27. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
\textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
H}, \textbf{Thomas F}, \textbf{Aboobaker A}, \textbf{Blaxter M}. 2016.
No evidence for extensive horizontal gene transfer in the genome of the
tardigrade hypsibius dujardini. bioRxiv 033464.
doi:\url{http://doi.org/10.1101/033464}.

\hyperdef{}{ref-Boothby2016}{\label{ref-Boothby2016}}
28. \textbf{Boothby TC}, \textbf{Goldstein B}. 2016. Reply to bemm et
al. and arakawa: Identifying foreign genes in independentHypsibius
dujardinigenome assemblies. Proceedings of the National Academy of
Sciences \textbf{113}:E3058--E3061.
doi:\url{http://doi.org/10.1073/pnas.1601149113}.

\hyperdef{}{ref-Koutsovoulos2016b}{\label{ref-Koutsovoulos2016b}}
29. \textbf{Koutsovoulos G}, \textbf{Kumar S}, \textbf{Laetsch DR},
\textbf{Stevens L}, \textbf{Daub J}, \textbf{Conlon C}, \textbf{Maroon
H}, \textbf{Thomas F}, \textbf{Aboobaker AA}, \textbf{Blaxter M}. 2016.
No evidence for extensive horizontal gene transfer in the genome of the
tardigradeHypsibius dujardini. Proceedings of the National Academy of
Sciences \textbf{113}:5053--5058.
doi:\url{http://doi.org/10.1073/pnas.1600338113}.
